### 2022-07-24 Paper/article3.tex
Final Version Article

The accurate forecast of stock prices, traded on an exchange, is inarguably one of the most challenging topics in the field of asset pricing. The stock market is described as an unpredictable, dynamic and non-linear construct. Predicting the prices of its stocks is an ambitious undertaking and depends on many variables including but not limited to the global economy, the company's metrics and local and global political situation. 
\\
\\
Historically there are two main prediction methods. The fundamental analysis which is a qualitative analysis of the company is interested in finding the true value of a stock and comparing it to the actual traded value. The evaluator utilizes several performance criteria e.g. the P/E ratio to truly assess the underlying stock. Secondly, the technical analysis, which is solely based on the past price of the stock e.g. in form of closing or opening prices as time-series. It is rather a short-term prediction using factors like the Moving Average (MA) or the Exponential Moving Average (EMA). Its basic assumption is that every significant information about the stock is already considered in the stock price \cite{prediction}.
\\
\\
The fast computational development has led to the point that Machine learning techniques have a significant application in financial problems. The use of artificial neural networks has found more and its way into the field of stock price prediction. Here a recurrent neural network (RNN) has been found very proven, more precisely the Long Short Term Memory (LSTM). Its advantage is being
able to process entire sequences of data rather than only one single data point. It has proven to be very practical with time series data such as our historical stock prices. 
\\
In this project, I create an application that is going to predict the \textbf{closing price} of any given stock on which it is trained. For the sake of convenience, this report only considers the stock price prediction of the \textbf{Apple} Inc. (\textit{\$AAPL}) stock.
\\
A train-test cycle is used to test the accuracy of the prediction. The root mean squared error (\ref{eq.rmse}) is used to measure the accuracy of the model:
\begin{equation}
RMSE = \sqrt{\dfrac{\Sigma_{i}(\hat{y}_i-y_i)}{N}} 
\label{eq.rmse}
\end{equation}
where $\hat{y}_i$ is the prediction of the $i-th$ stock price $y_i$ and $N$ is the total number of predicted stock prices.

@@

\begin{table}[H]
	\caption{The resulting $RMSE$ of the four models.}
	\centering
	\begin{tabular}{cr}
	\hline 
	Model & $RMSE$ \\ 
	\hline 
	simple & 37.83 \\ 
	refined 1 & 28.34 \\ 
	refined 2 & 9.59 \\ 
	refined 3 & 3.74 \\ 
	\hline 
	\end{tabular} 
	\label{tab:rsme}
\end{table}

@@

>>>>

The accurate forecast of stock prices, traded on an exchange, is inarguably one of the most challenging topics in the field of asset pricing. The stock market is described as an unpredictable, dynamic and non-linear construct. Predicting the prices of its stocks is an ambitious undertaking and depends on many variables including but not limited to the global economy, the company's metrics and local and global political situation. 
\\
\\
Historically there are two main prediction methods. The fundamental analysis which is a qualitative analysis of the company is interested in finding the true value of a stock and comparing it to the actual traded value. The evaluator utilizes several performance criteria e.g. the P/E ratio to truly assess the underlying stock. Secondly, the technical analysis, which is solely based on the past price of the stock e.g. in form of closing or opening prices as time-series. It is rather a short-term prediction using factors like the Moving Average (MA) or the Exponential Moving Average (EMA). Its basic assumption is that every significant information about the stock is already considered in the stock price \cite{prediction}.
\\
\\
The fast computational development has led to the point that Machine learning techniques have a significant application in financial problems. The use of artificial neural networks has found more and its way into the field of stock price prediction. Here a recurrent neural network (RNN) has been found very proven, more precisely the Long Short Term Memory (LSTM). Its advantage is being
able to process entire sequences of data rather than only one single data point. It has proven to be very practical with time series data such as our historical stock prices. 
\\
In this project, I create an application that is going to predict the \textbf{closing price} of any given stock on which it is trained. For the sake of convenience, this report only considers the stock price prediction of the \textbf{Apple} Inc. (\textit{\$AAPL}) stock.
\\
A train-test cycle is used to test the accuracy of the prediction. The root mean squared error (\ref{eq.rmse}) is used to measure the accuracy of the model:
\begin{equation}
RMSE = \sqrt{\dfrac{\Sigma_{i}(\hat{y}_i-y_i)}{N}} 
\label{eq.rmse}
\end{equation}
where $\hat{y}_i$ is the prediction of the $i-th$ stock price $y_i$ and $N$ is the total number of predicted stock prices. The RMSE is a good measure to compare prediction with actual values and makes it easier to compare different models

@@

\begin{table}[H]
	\caption{The resulting $RMSE$ of the four models.}
	\centering
	\begin{tabular}{cr}
	\hline 
	Model & $RMSE$ \\ 
	\hline 
	simple & 42.49 \\ 
	refined 1 & 28.34 \\ 
	refined 2 & 9.59 \\ 
	refined 3 & 3.74 \\ 
	\hline 
	\end{tabular} 
	\label{tab:rsme}
\end{table}

@@

Generating test and training sets were more complex than usual since I am dealing with time series data. Also, I needed to put together a timeframe of past stock prices as my feature variables with its corresponding stock price prediction. This was quite tricky to generate.
